linearGR_Models

### 2018-04-06 manuscriptAnalysis/linearGR_Models.Rmd
sort out isYOY in det model and downstream

```

@@

2a is best for BKT
2 is best for BNT
```{r}

#BKT
sppMod <- 1
dIn <- d %>% filter(species == sppMod)

mod1 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2a <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2b <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2c <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod3 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod4 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod4a <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod5 <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5) %>% rownames_to_column() %>% arrange(AIC)
```
For salmon  - need to get rid of 'river'
mod5 is best
```{r}

#ATS
sppMod <- 3
dIn <- d %>% filter(species == sppMod)

mod1 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2a <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2b <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod2c <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod3 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod4 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod4a <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

mod5 <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn )

AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5) %>% rownames_to_column() %>% arrange(AIC)
```

>>>>

mod <- list(list())
dIn <- list()

bySpecies <- d %>% group_by(species) %>% nest()
```

@@

2a is best for BKT
2 is best for BNT
```{r bkt}

#BKT
sppMod <- 1
dIn[[sppMod]] <- d %>% filter(species == sppMod)

mod[[sppMod]][[1]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[2]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[3]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[4]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[5]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[6]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[7]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[8]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         isYOY * river * season * ( length * countPStdBKT ) +
                         isYOY * river * season * ( length * countPStdBNT ) +
                         isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[9]] <- lmer( grLength ~ isYOY * river * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * river * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * river * season * ( tempStd * flowStd * length ) +
                         # isYOY * river * season * ( length * countPStdBKT ) +
                         # isYOY * river * season * ( length * countPStdBNT ) +
                         # isYOY * river * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[10]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                      #   isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[11]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn[[sppMod]] )

mod[[sppMod]][[12]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn[[sppMod]] )

(aic[[sppMod]] <- AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5,mod5a,mod5b,mod5c) %>% rownames_to_column() %>% arrange(AIC))
```

For salmon  - need to get rid of 'river'
mod5 is best
```{r}

#ATS
sppMod <- 3
dIn[[3]] <- d %>% filter(species == sppMod)

mod[[3]][[1]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[2]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[3]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[4]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[5]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[6]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[7]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[8]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         isYOY * season * ( length * countPStdBKT ) +
                         isYOY * season * ( length * countPStdBNT ) +
                         isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[9]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

@@

                         (1|ind), data = dIn[[3]] )

mod[[3]][[10]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                      #   isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn[[3]] )

mod[[3]][[11]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn[[3]] )

mod[[3]][[12]] <- lmer( grLength ~ isYOY * season * ( tempStd * flowStd * countPStdBKT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdBNT ) +
                         isYOY * season * ( tempStd * flowStd * countPStdATS ) +
                         isYOY * season * ( tempStd * flowStd * length ) +
                         # isYOY * season * ( length * countPStdBKT ) +
                         # isYOY * season * ( length * countPStdBNT ) +
                         # isYOY * season * ( length * countPStdATS ) +

                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBKT2 ) +
                       #  isYOY * season * ( tempStd2 * flowStd2 * countPStdBNT2 ) +
                         isYOY * season * ( tempStd2 * flowStd2 * countPStdATS2 ) +
                         # # isYOY * season * ( tempStd2 * flowStd2 * length2 ) + # model error with this line in
                         # isYOY * season * ( length2 * countPStdBKT2 ) +
                         # isYOY * season * ( length2 * countPStdBNT2 ) +
                         # isYOY * season * ( length2 * countPStdATS2 ) +

                         (1|ind), data = dIn[[3]] )

(aic[[sppMod]] <- AIC(mod1,mod2,mod2a,mod2b,mod2c,mod3,mod4,mod4a,mod5,mod5a,mod5b,mod5c) %>% rownames_to_column() %>% arrange(AIC))
```
